%\documentclass{article}
%\usepackage{enumitem}
%\begin{center} 
%{\large Submission note}
%\end{center}
%\begin{document}




\section{Submission Note}


%\noindent 
Some preliminary results of this article appeared in {\it IEEE/ACM
  2014 International Conference on Computer-Aided Design (ICCAD 2014)
}\cite{paper_here}. In this journal submission, we have made
significant changes over the conference version. We believe the
difference is more than 40\% over the conference version of this
work. The details of changes are summarized below:
\begin{enumerate}

\item First, we further proposed new way to solve the constrained
  nonlinear optimization in the conference version by reformulating
  the same problem into a mixed-integer linear programming (MILP)
  problem and found the better solutions under the same assumptions of
  the previous nonlinear programming problem. The new problem
  formulation is more novel and significant as its solution leads to
  nearly optimal solutions to the original constrained nonlinear
  problem.

\item For solution quality study and analysis, we compared the both
  optimization algorithms on a number of examples. We found the result
  indicated that the previously proposed constrained optimization can
  lead to near-optimal results in general.

\item We showed the Pareto-like trade-off between the performance and
lifetime. We also discussed the trade-off as long-term and short-term
reliability effects.

\item We completely rewrote the abstract, introduction, problem
sections to reflect the new scope of the article.

\item The content of the article, including the notations and figures,
have been substantially revised to improve the presentation.


\end{enumerate}



%\end{document}
