% v2-acmsmall-sample.tex, dated March 6 2012
% This is a sample file for ACM small trim journals
%
% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
% (c) 2010 Association for Computing Machinery (ACM)
%
% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
% Users can also go through the FAQs available on the journal's submission webpage.
%
% Steps to compile: latex, bibtex, latex latex
%
% For tracking purposes => this is v1.3 - March 2012

\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

\usepackage{epstopdf}
\epstopdfsetup{update}
\usepackage{epstopdf-base}

%\epstopdfDeclareGraphicsRule{.eps}{pdf}{.pdf}{%
%  ps2pdf -sEPSCrop #1 \OutputFile
% }


% Metadata Information
\acmVolume{9}
\acmNumber{4}
\acmArticle{39}
\acmYear{2010}
\acmMonth{3}

% Copyright
\setcopyright{rightsretained}

% DOI
\doi{0000001.0000001}

%ISSN
\issn{1234-56789}

\makeatletter
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
\usepackage{tabu}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcommand{\RN}[1]{%
  \textup{\uppercase\expandafter{\romannumeral#1}}%
}

\usepackage{cite}

\usepackage[cmex10]{amsmath}

\usepackage{multirow}

\usepackage{array}

\usepackage{url}

\usepackage{subfig}

\usepackage{booktabs}

%\usepackage{caption}

\hyphenation{op-tical net-works semi-conduc-tor}

\newcommand{\EP}{EnergyPlus}
\newcommand{\DegC}{$^\circ$C}


% Document starts
\begin{document}


% Title portion
\title{Thermal-Sensor-Based Occupancy Detection For Smart Buildings Using Machine Learning Methods}
\author{QI HUA
\affil{Shanghai Jiao Tong University}
HENGYANG ZhAO
\affil{University of Californiat at Riverside}
HAIBAO CHEN
\affil{Shanghai Jiao Tong University}
YAOYAO YE
\affil{Shanghai Jiao Tong University}
Hai Wang
\affil{University of Electronic Science and Technology of China}
SHELDON X.-D. TAN
\affil{University of California, Riverside}
XIN LI
\affil{Carnegie Mellon University}
ESTEBAN TLELO-CUAUTLE
\affil{INAOE and CINVESTAV, Mexico}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

\begin{abstract}

In this article, we propose a novel method to detect the occupancy behavior of a building through the temperature and/or possible heat source information, which can be used for energy reduction and security monitoring for emerging smart buildings. Our work is based on a realistic building simulation program, \EP{}, from Department of Energy.  \EP{} can model the various time-series inputs to a building such as ambient temperature, heating, ventilation, and air-conditioning (HVAC) inputs, power consumption of electronic equipment, lighting and number of occupants in a room sampled in each hour and produce resulting temperature traces of zones (rooms).

Three machine learning based approaches for detecting human occupancy of a smart building are applied herein, namely: support vector regression (SVR) method, forward neural network (FNN) method and recurrent neural network (RNN). Experimental results with SVR method show that 4-feature model provides accurate detection rate giving a 0.638 average error and 0.0532 error ratio, and 5-feature model gives a 0.317 average error and
0.0264 error ratio. This indicates that SVR is a viable option for occupancy detection. FNN method show that 5-feature model manifests similar accuracy on occupancy detection. In RNN method, Elman's RNN (ELNN) can estimate occupancy information of each room of a building with high accuracy. It has local feedbacks in each layer and for a 5-zones building it is very accurate for occupancy behavior estimation. The error level, in terms of number of people can be as low as 0.0056 on average and 0.288 at maximum considering ambient, room temperatures and HVAC powers as detectable information. Without knowing HVAC powers, the estimation error can still be 0.044 on average, and only 0.71\% estimated points have errors greater than 0.5.
\end{abstract}

\keywords{Smart building; support vector regression; neural network; indoor temperature; occupancy detection.}

\acmformat{Qi Hua, Hai-Bao Chen, Yao-Yao Ye, Sheldon X.-D. Tan, Xin Li, and Esteban Tlelo-Cuautle, 2016. Occupancy Detection in Smart Buildings Using Machine Learning Methods.}

% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.


\maketitle

\input intro.tex

\input energyplus_review.tex

\input machine_learning_review.tex

\input svm_nn_method_results.tex

\input rnn_method.tex

\input results.tex


\section{Conclusion}
A mathematical model based on SVR and neural network to detect employee occupancy in a smart
building, has been introduced. Three machine learning based occupancy detection methods for smart buildings through the thermal sensor temperature information and/or possible heat source information, have been discussed. In all experiments, we used the realistic building simulation program \EP{} to
collect training and validation datasets. Ambient factors, room
temperature, and/or HVAC power  were selected as features to train
Elman's recurrent neural network (ELNN). In SVR model, two sets of features are offered to feed off the model for
different conveniences. The first set of features is comprised of 4
features including solar factor, working time, indoor temperature and
outdoor temperature, which are regarded as easily obtained features;
whereas the second set of features adds light energy as the fifth
feature. In light of the experimental results, 4-feature model has a
quite accurate detection rate which gives a 0.638 average error and
0.0532 error ratio. However, 5-feature SVR model giving a 0.317
average error and 0.0264 error ratio has a better performance than
4-feature model, which we consider as moderating the under-fitting
issue. This indicates that using SVR model is a viable option when it comes
to occupancy detection given its convenience in data acquirement. In
neural network, only 5-feature model is established and it manifests
similar accuracy on occupancy detection.

In the recurrent neutral network based method, the resulting Elman
network can estimate occupancy information of each room of a building
with high accuracy. Using ambient factors and room temperatures only,
the average estimation error is 0.044, and only 0.71\% of the
estimated points have errors greater than 0.5 in terms of number of
people. This indicates that it is possible to precisely estimate the
occupancy only using ambient factors and room temperatures. With HVAC
powers added, the estimation can be even more accurate with even
simpler neural networks.

As a conclusion, what influences the model is the number of features and the number of data
points, virtually the two different methods SVR and ELNN work similarly well for
solving this problem. However, further improvement is likely to occur
when the model is refined to be able self-improved using current data
set in the future.



% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{title2,./building_model_sim}
                             % Sample .bib file with references that match those in
                             % the 'Specifications Document (V1.5)' as well containing
                             % 'legacy' bibs and bibs with 'alternate codings'.
                             % Gerry Murray - March 2012

% History dates
%\received{February 2007}{March 2009}{June 2009}

% Electronic Appendix
\elecappendix

\medskip



\end{document}
% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM


