% v2-acmsmall-sample.tex, dated March 6 2012
% This is a sample file for ACM small trim journals
%
% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
% (c) 2010 Association for Computing Machinery (ACM)
%
% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
% Users can also go through the FAQs available on the journal's submission webpage.
%
% Steps to compile: latex, bibtex, latex latex
%
% For tracking purposes => this is v1.3 - March 2012

\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information
\acmVolume{9}
\acmNumber{4}
\acmArticle{39}
\acmYear{2010}
\acmMonth{3}

% Copyright
\setcopyright{rightsretained}

% DOI
\doi{0000001.0000001}

%ISSN
\issn{1234-56789}

\makeatletter
\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother
\usepackage{tabu}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcommand{\RN}[1]{%
  \textup{\uppercase\expandafter{\romannumeral#1}}%
}

\usepackage{cite}

\usepackage[cmex10]{amsmath}

\usepackage{multirow}

\usepackage{array}

\usepackage{url}

\usepackage{subfig}

\usepackage{booktabs}

%\usepackage{caption}

\hyphenation{op-tical net-works semi-conduc-tor}

\newcommand{\EP}{EnergyPlus}
\newcommand{\DegC}{$^\circ$C}


% Document starts
\begin{document}


% Title portion
\title{Thermal-Sensor-Based Occupancy Detection For Smart Buildings Using Machine Learning Methods}
\author{QI HUA
\affil{Shanghai Jiao Tong University}
HENGYANG ZhAO
affil{University of Californiat at Riverside}
HAIBAO CHEN
\affil{Shanghai Jiao Tong University}
YAOYAO YE
\affil{Shanghai Jiao Tong University}
Hai Wang
\affil{University of Electronic Science and Technology of China}
SHELDON X.-D. TAN
\affil{University of California, Riverside}
XIN LI
\affil{Carnegie Mellon University}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

\begin{abstract} 

In this article, we propose a novel method to detect the occupancy
  behavior of a building through the temperature and/or possible heat
  source information, which can be used for energy reduction, security
  monitoring for emerging smart buildings. Our work is based on a
  realistic building simulation program, \EP{}, from Department of
  Energy.  \EP{} can model the various time-series inputs to a
  building such as ambient temperature, heating, ventilation, and
  air-conditioning (HVAC) inputs, power consumption of electronic
  equipment, lighting and number of occupants in a room sampled in
  each hour and produce resulting temperature traces of zones (rooms).
 In this paper, we studies three machine learning based approaches for
 detecting human occupancy of a smart building: The support vector
 regression (SVR) method, the forward neural network (FNN) method and
 the recurent neutral network (RNN). 
% The model is able to
%   detect occupancy with two sets of features corresponding to
%   different degrees of convenience. 
% The feature pool is comprised of
%   solar factor, working time, lights energy, indoor temperature, and
%   outdoor temperature. We show
%   different results by setting different parameter values in the
%   model, and demonstrate model comparison on occupant detection. 
  For the RNN-based method, we
  applied the Elman's recurrent neural network (ELNN), which has local
  feedbacks in each layer. We use an empirical formula to calculate
  the RNN layer number and layer size to configure RNN architecture to
  avoid overfitting and under-fitting problems. Experimental results
  from a case study of a 5-zone building show that ELNN can lead to
  very accurate occupancy behavior estimation. The error level, in
  terms of number of people, can be as low as 0.0056 on average and
  0.288 at maximum when we consider ambient, room temperatures and
  HVAC powers as detectable information. Without knowing HVAC powers,
  estimation error can still be 0.044 on average, and only 0.71\%
  estimated points have errors greater than 0.5.

Among the three methods, we show that xxx
  % The
  % proposed model displays advantages in occupancy detection which is
  % capable of making accurate detections at low requirements for sensor
  % accuracy and reducing the equipment cost in smart buildings.
\end{abstract}

\keywords{Smart building; support vector regression; neural network; indoor temperature; occupancy detection.}

\acmformat{Qi Hua, Hai-Bao Chen, Yao-Yao Ye, Sheldon X.-D. Tan, and Xin Li, 2016. Occupancy Detection in Smart Buildings Using Machine Learning Methods.}

% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.


\maketitle

\input intro.tex

\input energyplus_review.tex

\input machine_learning_review.tex

\input svm_nn_method_results.tex

\input rnn_method.tex

\input results.tex


\section{Conclusion}
In this paper, we propose a mathematical model respectively based on
SVR and neural network to detect employee occupancy in a smart
building.

In this article, we propose a a number of machine learning based
occupany detection methods for smart buildings through the thermal
sensor temperature information and/or possible heat source
information. We use a realistic building simulation program \EP{} to
collect training and validation datasets. Ambient factors, room
temperature, and/or HVAC power are selected as features to train the
Elman recurrent neural network. We studied three methods. In SVR
model, two sets of features are offered to feed off the model for
different conveniences. The first set of feature is comprised of 4
features including solar factor, working time, indoor temperature and
outdoor temperature which are regarded as easily obtained features
whereas the second set of features adds light energy as the fifth
feature. In light of the experimental results, 4-feature model has a
quite accurate detection rate which gives a 0.638 average error and
0.0532 error ratio. However, 5-feature SVR model giving a 0.317
average error and 0.0264 error ratio has a better performance than
4-feature model which we consider as moderating the under-fitting
issue. This indicates using SVR model is a viable option when it comes
to occupancy detection given its convenience in data acquirement. In
neural network, only 5-feature model is established and it manifests
similar accuracy on occupancy detection.

A conclusion is drawn in this model that, what
influences the model more is the features and the number of data
points, virtually the two different methods work similarly well for
solving this problem. However, further improvement is likely to occur
when the model is refined to be able self-improved using current data
set in the future.

In the recurrent neutral network based method, the resulting Elman
network can estimate occupancy information of each room of a building
with high accuracy. Using ambient factors and room temperatures only,
the average estimation error is 0.044, and only 0.71\% of the
estimated points have errors greater than 0.5 in terms of number of
people. This indicates that it is possible to precisely estimate the
occupancy only using ambient factors and room temperatures. With HVAC
powers added, the estimation can be even more accurate with even
simpler neural network.

% Bibliography
\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{title2,./building_model_sim}
                             % Sample .bib file with references that match those in
                             % the 'Specifications Document (V1.5)' as well containing
                             % 'legacy' bibs and bibs with 'alternate codings'.
                             % Gerry Murray - March 2012

% History dates
%\received{February 2007}{March 2009}{June 2009}

% Electronic Appendix
\elecappendix

\medskip



\end{document}
% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM


